\documentclass{article}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\usepackage[accepted]{icml2025}

\definecolor{TUred}{RGB}{165,30,55}
\definecolor{TUdark}{RGB}{50,65,75}
\definecolor{TUblue}{RGB}{0,105,170}
\definecolor{TUgold}{RGB}{180,160,105}
\definecolor{TUgreen}{RGB}{125,165,75}
\setlength{\floatsep}{6pt}
\setlength{\textfloatsep}{7pt}
\setlength{\intextsep}{5pt}
\setlength{\abovecaptionskip}{3pt}
\setlength{\belowcaptionskip}{0pt}
\icmltitlerunning{A Focused Search Engine for Tübingen}

\begin{document}
\twocolumn[
\icmltitle{A Focused Search Engine for English Tübingen Content}
\begin{icmlauthorlist}
\icmlauthor{TODO: authors}{equal}
\end{icmlauthorlist}
\icmlaffiliation{equal}{TODO: student IDs, degree programmes, and university email addresses}
\icmlkeywords{focused crawling, BM25F, hybrid retrieval, search interface}
\vskip 0.2in
]

\begin{abstract}
We built an end-to-end search engine for English web pages about Tübingen.
It combines a focused, resumable crawler with a field-weighted lexical index,
term-proximity scoring, passage-level semantic re-ranking, and an interactive
constellation interface. A controlled 15-query experiment improved
$\mathrm{nDCG}@10$ from 0.599 to 0.655. The current 20-query system reaches
$\mathrm{nDCG}@10=0.688$ at 34.9\,ms mean measured retrieval latency. These
results are promising, but the judgments were pooled from system outputs and
were not assessed independently.
\end{abstract}

\section{Scope and Architecture}
The system targets English pages that are relevant to Tübingen. It owns the
complete path from URL discovery to presentation. Figure~\ref{fig:architecture}
shows the deployed data flow. Components exchange files and SQLite records;
the query service loads the index once at startup. This keeps crawling,
offline indexing, and online retrieval independently runnable.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
  node distance=3.5mm and 4.5mm,
  box/.style={draw=TUdark,rounded corners,fill=TUblue!7,minimum height=6mm,
    align=center,font=\scriptsize,inner xsep=4pt},
  arr/.style={-{Latex[length=2mm]},semithick,TUdark}]
\node[box] (seed) {Seeds};
\node[box,right=of seed] (crawl) {Focused\\crawler};
\node[box,right=of crawl] (store) {HTML +\\SQLite};
\node[box,right=of store] (index) {BM25F index +\\passage vectors};
\node[box,below=of index] (api) {FastAPI\\query service};
\node[box,left=of api] (ui) {React/Three.js\\interface};
\draw[arr] (seed)--(crawl);
\draw[arr] (crawl)--(store);
\draw[arr] (store)--(index);
\draw[arr] (index)--(api);
\draw[arr] (api)--(ui);
\end{tikzpicture}}
\caption{Implemented architecture. Offline stages are on top; online stages
are below.}
\label{fig:architecture}
\end{figure}

\section{Focused Crawling}
One global priority frontier schedules URLs across hosts. It admits at most
one concurrent request per host and applies configurable request delays.
Before fetching, the crawler evaluates \texttt{robots.txt}; the Robots
Exclusion Protocol defines publisher rules for automated clients
\cite{koster2022robots}. HTTP 429 and server errors trigger bounded retries.
Frontier and deduplication state are persisted, so interrupted crawls resume.

Two local classifiers focus the crawl. \emph{LinkVerdict} scores candidate
links from their anchor, target, parent, depth, and parent verdict.
\emph{PageVerdict} scores fetched content and admits only English pages above
a fixed threshold. Per-page, host, URL-family, depth, and rejection budgets
limit traps and concentration. A small exploration lane admits up to three
lower-confidence links per page from previously unproductive hosts.

Canonical URLs prevent exact revisits. A text SimHash removes near-duplicate
pages; SimHash is established for large-scale web near-duplicate detection
\cite{manku2007simhash}. HTML is stored on disk, while page, link, decision,
and model metadata are stored in SQLite. The archived 20 July crawl fetched
8,290 pages from 231 hosts, saved 3,475 (41.9\%), and rejected 823 duplicates
(9.9\% of fetches). These are descriptive crawl statistics, not relevance
precision estimates.

\section{Indexing and Retrieval}
The tokenizer lowercases alphanumeric English tokens, removes one-character
tokens, and filters English stopwords while retaining negations. The inverted
index stores postings and body positions. Ranking starts with BM25F over body,
title, and URL-path fields, weighted 1, 5, and 3. BM25F extends BM25 to
weighted document fields with field-length normalization
\cite{robertson2004bm25f}. A maximum-window bonus of
$0.25/(1+\mathrm{gap})$ rewards documents in which all matched query terms
occur close together. Combining proximity evidence with Okapi-style scoring
has prior support \cite{rasolofo2003proximity}.

Semantic retrieval uses \texttt{nli-mpnet-base-v2}. Sentence-BERT-style
models encode text into vectors suitable for cosine comparison
\cite{reimers2019sentencebert}. Documents are split into overlapping passages;
the best passage score represents each document. The candidate union contains
the top 100 lexical and top 100 semantic results. Final scores are
$0.85\,s_{lex}+0.15\,s_{sem}$, where the lexical score is min--max normalized.
Convex score fusion is simple, tunable with one parameter, and has outperformed
reciprocal-rank fusion in published hybrid-retrieval experiments
\cite{bruch2023fusion}. Missing or stale vectors safely fall back to lexical
ranking. The CLI also reads and writes the required tab-separated batch format.

\section{Result Presentation}
The FastAPI service exposes search and health endpoints. The React client
offers both a conventional ranked list and an interactive 3-D constellation.
Each result is a clickable star. Size and brightness encode normalized
relevance. Two fixed semantic axes---``university, research and
administration'' and ``tourism, culture and everyday life''---set the spatial
coordinates. Nearby stars expand on hover; ten results form one paged cluster.
This view exposes topical structure without changing the ranking.

\begin{figure}[t]
\centering
\begin{tikzpicture}[x=0.72cm,y=0.48cm,font=\scriptsize]
  \fill[TUdark] (0,0) rectangle (8,4.6);
  \draw[white!35] (4,0.5)--(4,4.0) (0.6,2.25)--(7.5,2.25);
  \node[white!70,anchor=south] at (4,4.0) {tourism / everyday life};
  \node[white!70,anchor=north] at (4,0.5) {research / administration};
  \foreach \x/\y/\r/\c in {1.4/3.2/2.2/TUgold,2.6/2.8/1.5/white,
    5.8/3.4/2.5/TUgold,6.7/1.5/1.8/white,4.8/1.1/1.3/TUblue,
    3.6/2.0/1.0/white} \fill[\c] (\x,\y) circle (\r pt);
  \node[white,anchor=west] at (0.5,4.3) {Search Tübingen\ldots};
\end{tikzpicture}
\caption{Placeholder for the final UI screenshot. Replace this schematic
before submission.}
\label{fig:ui}
\end{figure}

\section{Evaluation}
We use graded relevance judgments (0--3) and report nDCG, reciprocal rank,
positive results, judged coverage, and latency. nDCG discounts relevant items
at lower ranks and supports graded judgments \cite{jarvelin2002ndcg}.
The controlled ablation in Table~\ref{tab:results} uses the same crawl and 15
queries. Stopword filtering produced the largest gain; proximity added another
0.012 nDCG@10. Mean lexical latency remained below 2\,ms.

\begin{table}[t]
\centering
\caption{Controlled retrieval ablation (15 queries, one crawl snapshot).}
\label{tab:results}
\scriptsize
\setlength{\tabcolsep}{3.5pt}
\begin{tabular}{@{}lrrrr@{}}
\toprule
Variant & nDCG@10 & nDCG@20 & MRR@10 & Pos.@10\\
\midrule
BM25 baseline & .599 & .764 & .967 & 7.0\\
+ stopwords & .643 & .775 & 1.000 & 7.4\\
+ proximity & \textbf{.655} & .772 & 1.000 & \textbf{7.6}\\
\bottomrule
\end{tabular}
\end{table}

The current 20-query run reports nDCG@10 0.688, nDCG@20 0.694, MRR@10
0.900, 8.25 positives@10, and 34.9\,ms mean latency. It cannot be compared
directly with Table~\ref{tab:results}: both the crawl and judgment pool differ.
Moreover, judgments were created from the evaluated runs, which explains very
high judged coverage and risks pooling bias. No significance test or external
assessor study is available.

\section{Decisions, Limits, and Next Evidence}
The design favors transparent first-stage retrieval and confines learned
signals to crawl filtering and second-stage re-ranking. Offline embeddings
bound online work; lexical fallback preserves availability. The constellation
adds exploration while retaining a ranked list for direct navigation.

\textbf{TODO before submission:} add author and contribution details; replace
Figure~\ref{fig:ui} with a real screenshot; document classifier training data,
held-out metrics, and release identifiers; evaluate lexical versus hybrid
ranking on one frozen crawl with independent judgments and confidence
intervals; report index size, embedding build time, and end-to-end API latency.

\section{Conclusion}
The project implements a complete focused search engine with measurable
retrieval improvements. On a controlled snapshot, stopword filtering and
proximity improved nDCG@10 by 0.056 over the baseline. The current hybrid
system is operational, but its incremental value remains unproven until a
frozen, independently judged ablation is run.

\clearpage
\begin{thebibliography}{7}
\bibitem[Robertson et~al.(2004)]{robertson2004bm25f}
S. Robertson, H. Zaragoza, and M. Taylor. Simple BM25 extension to multiple
weighted fields. In \emph{CIKM}, 2004.

\bibitem[Rasolofo and Savoy(2003)]{rasolofo2003proximity}
Y. Rasolofo and J. Savoy. Term proximity scoring for keyword-based retrieval
systems. In \emph{ECIR}, 2003.

\bibitem[Manku et~al.(2007)]{manku2007simhash}
G. Manku, A. Jain, and A. Das Sarma. Detecting near-duplicates for web
crawling. In \emph{WWW}, 2007.

\bibitem[Koster et~al.(2022)]{koster2022robots}
M. Koster, G. Illyes, H. Zeller, and L. Sassman. Robots Exclusion Protocol.
RFC 9309, 2022. \url{https://www.rfc-editor.org/rfc/rfc9309}

\bibitem[Reimers and Gurevych(2019)]{reimers2019sentencebert}
N. Reimers and I. Gurevych. Sentence-BERT: Sentence embeddings using Siamese
BERT-networks. In \emph{EMNLP-IJCNLP}, 2019.

\bibitem[Bruch et~al.(2023)]{bruch2023fusion}
S. Bruch, S. Gai, and A. Ingber. An analysis of fusion functions for hybrid
retrieval. \emph{ACM Transactions on Information Systems}, 2023.

\bibitem[J\"arvelin and Kek\"al\"ainen(2002)]{jarvelin2002ndcg}
K. J\"arvelin and J. Kek\"al\"ainen. Cumulated gain-based evaluation of IR
techniques. \emph{ACM Transactions on Information Systems}, 2002.
\end{thebibliography}
\end{document}
